\section{Related Work}

\textbf{Financial and agent benchmarks.} Financial benchmarks evaluate numerical reasoning, language understanding, forecasting, and decision support~\cite{chen2021finqa,xie2023pixiu,xie2024finben,wu2023bloomberggpt,liu2021finrl}. General agent benchmarks evaluate task completion, browsing, and tool use~\cite{liu2023agentbench,zhou2023webarena,qin2023toolllm,mialon2023gaia,yao2023react}. These resources establish important capability measurements, but their evaluation unit is generally a prediction, answer, or completed trajectory rather than the validity of an execution-authority benchmark. Supplementary Table~\ref{tab:benchmark_comparison} locates FinAuth-Audit along that distinction.

\textbf{Selective decisions and safe evaluation.} Selective classification studies prediction with abstention~\cite{elyaniv2010foundations,geifman2017selective}; conformal methods provide distribution-free uncertainty statements under stated assumptions~\cite{vovk2005algorithmic,shafer2008tutorial,angelopoulos2021gentle}; off-policy evaluation estimates policy value from logged behavior~\cite{dudik2011doubly,jiang2016doubly,thomas2016data}; and safe reinforcement learning studies constrained sequential decisions~\cite{garcia2015comprehensive,tamar2015policy}. FinAuth-Audit does not replace these methods. It audits whether a benchmark can distinguish genuine authorization quality from zero coverage, authority leakage, and invalid transfer.

\textbf{Benchmark and model-risk validity.} Benchmark fragility, behavioral testing, measurement validity, data documentation, and shortcut learning motivate stronger evaluation contracts~\cite{dehghani2021benchmark,kiela2021dynabench,ribeiro2020checklist,jacobs2021measurement,gebru2021datasheets,sambasivan2021data,geirhos2020shortcut}. Financial model-risk guidance likewise emphasizes validation, controls, and traceable reporting~\cite{board2011sr117,bis2013principles}. The closest decision-rule perspective evaluates choices across many weak experiments~\cite{chou2025weakrules,bibaut2024covariance,tripuraneni2024choosing}. FinAuth-Audit changes the unit from business experiments to weak financial priors and adds execution coverage, source provenance, point-in-time transfer, and mechanism-level training validity.
