\section{Use, Limitations, and Research Opportunities}

\textbf{Community use.} External researchers can implement a rule against the legal feature manifest and run the same cluster-aware certification, provenance, power, and mechanism-coverage checks. The release records field access, four-way routes, hashes, and structural \textit{N/A}. The 5,000-cluster community-hidden partition remains unevaluated under versioned maintenance.

\textbf{From controlled evaluation to deployment.} The controlled layers are authorization scenarios, not price-path simulations, institutional logs, or human labels. Branch-neutral construction and the frozen test improve internal validity, while prospective generators expose mechanism sensitivity. Because all generators share authorship and legal-field design, conclusions remain conditional on the released scenarios and do not establish practitioner agreement or deployment readiness.

\textbf{External and review limits.} Binance adds observed spread and depth. Planning variance is transported, constructed priors remain in v0.3, and only one arm passes. The v0.6 layer adds actual model proposals across five assets and two tasks, but legal source roles remain benchmark-assigned and the study does not observe institutional permission. Its 200 dates support aggregate inference but not precise model- or asset-specific rankings. The holdout snapshot is self-custodied ciphertext rather than third-party escrow, and model aliases can drift after generation. MES is licensed, single-instrument, underpowered, and has one non-estimand role contrast. Event-market, FRED, and GDELT evidence remains non-confirmatory; no source provides practitioner labels or broad generalization. Review load and cost are simulated, not observed staffing performance.

\textbf{What the validity gates show.} Across 144 prospective fits, broader data recover five of six mechanisms, while sequential-market coverage remains unresolved. The actual-proposal audit shows why the release protocol matters: a dramatic 60-date pilot inversion did not survive the larger preregistered test, and development-only threshold recalibration did not uniformly improve authority quality. Coverage-constrained objectives, independently authored generators, practitioner-labelled authorization tasks, and stronger point-in-time data can be added without changing the frozen paper test. FinAuth-Audit remains an offline research benchmark, not investment advice or institutional approval.
