\documentclass[sigconf,review,screen]{acmart}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{placeins}

\definecolor{FinAuthLinkBlue}{HTML}{1F5AA6}

% Give narrow ACM columns enough flexibility to avoid isolated short overfull
% lines without shrinking the document font or scaling tables.
\setlength{\emergencystretch}{2em}

\newcommand{\benchmarktableformat}{%
  \small
  \setlength{\tabcolsep}{4.5pt}%
  \renewcommand{\arraystretch}{1.08}%
}

\setcopyright{none}
\settopmatter{printacmref=true, printccs=true, printfolios=true, authorsperrow=2}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\acmConference[KDD '27]{The 33rd ACM SIGKDD Conference on Knowledge Discovery and Data Mining}{August 1--5, 2027}{San Jose, CA, USA}
\acmYear{2027}
\copyrightyear{2027}

\title{FinAuth-Audit: Validity-Aware Benchmarking of Financial Agent Authorization}
\input{author_metadata}
\input{generated/claims_real_agent_v06}

\begin{abstract}
Financial agents turn weak priors into actions, but outcome loss, policy violation, and execution authority are distinct. FinAuth-Audit benchmarks whether comparisons among execution rules remain valid when coverage, provenance, consequence severity, review workload, utility, and point-in-time evidence are audited jointly. We benchmark execution rules, not predictors. The release contains 124,000 controlled, provenance, and mechanistic event clusters, public event and order-book layers, and a preregistered 300-date actual-model partition. Four findings define the benchmark. First, the lowest negative-utility authorization rate (NUAR; the frozen artifact field is retained as legacy \texttt{FAR}) is 0.064 but coexists with ALR 0.245, while lineage-clean rules occupy different coverage, utility, and review frontiers. Second, a clean current role retains 0.172 indirect laundering, and partial lineage signatures leave a nonzero finite-sample information cost. Third, a 200-date actual-model test does not reproduce a 60-date pilot inversion and shows that economic loss, material harm, and authority violation rank operating points differently. Fourth, predeclared validity gates retain a powered mixed Binance result, an underpowered event-market layer, and coverage-collapsed learner comparisons rather than promoting partial evidence. FinAuth-Audit provides frozen splits, legal-field manifests, one-time paper tests, hidden challenges, and content-addressed verification. Code, released benchmark artifacts, manifests, and verification scripts are available at \url{https://github.com/colin-wang-research/finanth-audit}. It is an offline benchmark and release protocol, not a trading strategy, deployment claim, or investment recommendation.
\end{abstract}

\keywords{financial agents, execution authorization, benchmark validity, provenance auditing, abstention, agent safety}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257</concept_id>
<concept_desc>Computing methodologies~Machine learning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010489</concept_id>
<concept_desc>Applied computing~Economics</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Computing methodologies~Machine learning}
\ccsdesc[300]{Applied computing~Economics}

\begin{document}
% acmart applies its own hyperlink defaults at document start. Set the public
% paper palette here so URLs, citations, and cross-references remain visibly
% distinct in the generated PDF.
\hypersetup{%
  linkcolor=FinAuthLinkBlue,
  citecolor=FinAuthLinkBlue,
  urlcolor=FinAuthLinkBlue,
  filecolor=FinAuthLinkBlue
}
\maketitle

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_task_model}
\input{sections/04_construction}
\input{sections/05_protocol}
\input{sections/06_results}
\input{sections/07_discussion}
\input{sections/08_conclusion}

\FloatBarrier
\clearpage
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\clearpage
\appendix
\raggedbottom
\input{supplement}

\end{document}
